Naturalness in U(1) exentions of the MSSM

### 2014-11-07 paper/e6ssm-tuning-paper.tex
changed title. started to sketch out introduction and added references.

\title{Fine tuning in the E$_6$SSM}

\author{P. Athron}
 \email{peter.athron@adelaide.edu.au}
 \affiliation{
ARC Centre of Excellence for Particle Physics at the Terascale, School of Chemistry and Physics, The University of Adelaide,
Adelaide, South Australia 5005, Australia}

@@

\section{\label{sec:intro}Introduction}

@@

% NB before submission replace this with a copy-paste of the bbl file?
\bibliography{bibliography}
\end{document}

>>>>

\title{Naturalness in U(1) exentions of the MSSM}

\author{P. Athron}
 \email{peter.athron@adelaide.edu.au}
 \affiliation{
ARC Centre of Excellence for Particle Physics at the Terascale, School of Physics, Monash University, Melbourne VIC 3800, Australia
}

@@

\section{\label{sec:intro}Introduction}
The discovery of an approximately 125 GeV Higgs
\cite{Aad:2012tfa,Chatrchyan:2012ufa} at the large hadron collider
(LHC) has interesting implications for physics beyond the standard
model (SM) and supersymmetry (SUSY).  On the one hand it provides a
light Higgs boson in fitting with expectations from supersymmetry, and
can be fitted in the minimal supersymmetric standard model (MSSM).  On
the other hand it is slightly heavier than the constrained versions of the 
MSSM (cMSSM) can accommodate naturally \cite{Cassel:2011zd,Ghilencea:2012gz}.

The Higgs causes a naturalness problem because at tree level it has an
upper bound of $m_Z$. The dominant higher order corrections to the
Higgs mass come from stops and to obtain a $125$ GeV Higgs they need
be rather heavy. Heavy stops will provide a large contribution to the
soft breaking mass for the up-type Higgs scalar, $m_{H_u}^2$ at low
energies, through the evolution of the renormalisation group equations
(RGEs) from the grand unification (GUT) scale to the electroweak (EW)
scale. This affects the SUSY prediction of the electroweak VEV, v, or
the mass of the $Z$ boson, $m_Z$.  This naturalness problem motivates
both further examination of non-minimal SUSY models that can raise the
Higgs mass without the need for heavy stops and alternative
possibilities for how the soft breaking parameters get generated,
which might set them them at lower energies, reducing the influence
the stops have on the soft breaking mass for the up-type Higgs scalar,
$m_{H_u}^2$.

In addition to that naturalness issue, often referred to as the little
hierarchy problem, the MSSM also suffers fromn the $\mu$-problem. This
is also a naturalness problem since there should be a natural explanation
of how the $\mu$ superpotential parameter can be set to the same scale
as the soft breaking masses.

U(1) extensions of the MSSM provide a very elegant solution to this
$\mu$-problem \cite{} and also raise the Higgs mass with new $F$- and
$D$-terms. Nonetheless, as was recently demonstrated in the context of
the exceptional supersymmetric standard model (E$_6$SSM)
\cite{King:2005jy,King:2005my,Athron:2010zz}, can still suffer from
naturalness problems with the mass of the new $Z^\prime$ associated
with break down of the new U(1) appearing in the electroweak symmetry
breaking conditions at tree level \cite{Athron:2013ipa}.  Nonetheless
the constrained version of E$_6$SSM (cE$_6$SSM) \cite{Athron:2009ue,
  Athron:2009bs} still turned out to be significantly less tuned than
the cMSSM.

However this comparison of fine tuning depends crucially upon the
assumptions of these gravity mediated SUSY breaking motivated
constrained models and in particular the way the universality
constraints are applied at the GUT scale.  As mentioned above, given
the findings at the LHC it is worth considering other possibilities,
which may allow the soft masses to be set at lower energies. As the
scale at which the parameters fufill some breaking inspired
constraints is lowered the stop masses contribute less to the fine
tuning.

At the same time in U(1) extensions, lowering the UV boundary scale
for the RGE evolution also allows even larger $F$-term contriubutions
to the Higgs mass, so long as one only requires $\lambda$, the
coupling between the Singlet Higgs, $S$ and the up- and down-type
Higgs bosons, $H_u$ and $H_d$, to remain perbative up to the UV scale
and not the all teh up to the GUT scale.

However the tuning from the
$Z^\prime$ mass limit does not disappear as the UV boundary condition is lowered. This tuning  appears in the EWSB conditions at tree level and is quite difficult to avoid without introducing a pure gauge singlet \cite{Athron:2014pua}.

In this paper we investigate how big this tuning is if we bring this
scale all the way down to 20 TeV, effectively minimising contribution
from the stops. We find that the $Z^\prime$ limit is enough to already
require moderate fine tuning.  We also show this is comparable to the
situation in the MSSM defined at smae scalew if chargino limit is
$700$ GeV, which is the most conservative limit on can obtain and
above the tuning from the stops, in both the MSSM and U(1) extensions.
We also show that the tuning from the stops becomes larger when the
high scale is raied to ?? wheares for the E$_6$SSM the minimum tuning
is lower than the MSSM above this scale.  Therefore iot is clear that
which model is preferred and how large the tuning is depends on our
assumptions about SUSY breaking models.

However we also show that if the $Z^\prime$ limit is the extended to
?? then $U(1)$ extensions of the MSSM will already suffer from a
severe tuning, irrespectiove of the UV boundary condition for th RGE
evolution.  Therefore the $Z^\prime$ constraint is amongst the most
important in terms of tuning and attacking natural supersymmtry
experimentally and the next run of the LHC will be crucial.

U(1) literature review  \newline

E6 literature review \newline
 Exceptional Supersymmetric Standard Model is a very well U(1) extension where....

fine tuning literature review... \newline  It has also been shown that the NMSSM is less fine tuned than in it's minimal model rather than with the inclusion of extra matter \cite{Binjonaid:2014oga}.  \newline

summary of paper

@@

% NB before submission replace this with a copy-paste of the bbl file?
\bibliography{bibliography}{}
\end{document}
